---
title: "Decentralized Construct Taxonomies"
author: "Gjalt-Jorn Ygram Peters"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In psychology, many different guidelines exist for
    developing measurement instruments and manipulations of constructs.
    When conducting empirical research or secondary research,
    therefore, it is important to have a clear idea, and clearly
    communicate, which guidelines are followed. However, these guidelines
    are fragmented, and no universal consensus exists regarding how any
    construct must be measured or manipulated. Therefore, developing one
    'final' taxonomy is not feasible or even desirable. At the same time,
    it is important that people clearly communicate their 'study-specific
    taxonomy'. The `dct` package makes it possible to combine these two
    goals.

For more background information on the concept of Decentralized Construct Taxonomies, see the reasoning set out in Peters & Crutzen (2017a, 2017b) and Crutzen & Peters (2018). In brief, in those papers the following premises are postulated:

- Psychological constructs do not exist as such, but instead are useful metaphors that enable communication about, and measurement and manipulation of, aspects of the human psychology.
- These constructs have verying degrees of specificity and levels of aggregation, and are therefore often represented in theories as influencing or causing one another.

From these premises it follows that is is not feasible (or desirable) to develop one 'final' taxonomy of psychological constructs or of manipulations of psychological constructs. Instead, multiple taxonomies exist, each of which has different uses. For example, in behavior change research, one taxonomy has been developed that is well-suited for describing intervention content but that is not useful when developing interventions (Abraham & Michie, 2008), and another that is well-suited for developing interventions, but is in its present form less useful for coding interventions (Kok et al., 2016).

Similarly, different theories that explain behavior postulate 

For example, the heterogeneity in definitions and measurement instrument of self-efficacy has been lamented (Williams & Rhodes, 2016a, 2016b).



While the 

As a consequence of this pluriformity 

However, at the same time there is a need for consistency in communication.



## References

Abraham, C., & Michie, S. (2008). A taxonomy of behavior change techniques used in interventions. Health Psychology, 27(3), 379–87. doi: [10.1037/0278-6133.27.3.379](https://doi.org/10.1037/0278-6133.27.3.379)

Crutzen, R., & Peters, G.-J. Y. (2018). Evolutionary learning processes as the foundation for behaviour change. *Health Psychology Review*, 12(1), 43–57. doi: [10.1080/17437199.2017.1362569](https://doi.org/10.1080/17437199.2017.1362569)

Kok, G., Gottlieb, N. H., Peters, G.-J. Y., Mullen, P. D., Parcel, G. S., Ruiter, R. A. C., … Bartholomew, L. K. (2016). A taxonomy of behavior change methods: an Intervention Mapping approach. Health Psychology Review, 10(3), 297–312. doi: [10.1080/17437199.2015.1077155](https://doi.org/10.1080/17437199.2015.1077155)

Peters, G.-J. Y., & Crutzen, R. (2017a). Pragmatic nihilism: how a Theory of Nothing can help health psychology progress. *Health Psychology Review*, 11(2). doi: [10.1080/17437199.2017.1284015](https://doi.org/10.1080/17437199.2017.1284015)

Peters, G.-J. Y., & Crutzen, R. (2017b). Confidence in constant progress: or how pragmatic nihilism encourages optimism through modesty. *Health Psychology Review,* 11(2), 140–144. doi: [10.1080/17437199.2017.1316674](https://doi.org/10.1080/17437199.2017.1316674)

Williams, D. M., & Rhodes, R. E. (2016a). The confounded self-efficacy construct: review, conceptual analysis, and recommendations for future research. Health Psychology Review, 10(2), 113–128. doi: [10.1080/17437199.2014.941998](https://doi.org/10.1080/17437199.2014.941998)

Williams, D. M., & Rhodes, R. E. (2016b). Reviving the critical distinction between perceived capability and motivation: A response to commentaries. Health Psychology Review, 7199(April), 1–7. doi: [10.1080/17437199.2016.1171729](https://doi.org/10.1080/17437199.2016.1171729)




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
